Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2014-10-01 exp1/present2013.tex
reintroduce smaller things
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@766 43ef1190-90fd-4dd7-a769-d0121f02b80e

  \begin{itemize}
  \item The main effect of a 2-level factor is the average of the
    observed values on the second level minus the corresponding
    average of the first.
  \item Interaction effects may be complex, like one implementation is
    better on CONSTRUCT queries, on small datasets
\end{itemize}
}

@@

\begin{frame}{The experiments}

@@

\note{
  \begin{itemize}
% TODO: Lenth
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
    to that many more triples need to be searched for a language tag
    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit.
  \item We want to do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine'', in the paper we describe how this
    enables us to average over certain factors and look upon the rest
    as a replicated experiment.
  \end{itemize}
}

>>>>

  \begin{itemize}
  \item The main effect of a 2-level factor is the average of the
    observed values on the second level minus the corresponding
    average of the first.
  \item Interaction effects may be complex, like one implementation is
    better on CONSTRUCT queries, on small datasets
  \item We still need to understand which effects are important and
    significant, we do that in the discussion of our experiment

\end{itemize}
}

@@

\begin{frame}{Constraints on scope of experiment}

@@

\note{
  \begin{itemize}
% TODO: Lenth
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
    to that many more triples need to be searched for a language tag
    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit.
  \item We want to do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine''.
  \end{itemize}
}
